---
title: "Analysis of Models"
author: "Joel Larwood"
date: "01/12/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(emmeans) # Estimated Marginal Means, aka Least-Squares Means
library(readr) # Read Rectangular Text Data
library(ggplot2) # Create Elegant Data Visualisations Using the Grammar of Graphics
library(magrittr) # A Forward-Pipe Operator for R
```

```{r}
data <- here::here( # this data is for the RT measure
  "results",
  "data",
  "modelling_data",
  "modelling_data_acc.rds"
) %>% 
  read_rds()

data_agg <- here::here( # this data is for the d' measure
  "results",
  "data",
  "modelling_data",
  "modelling_data_d.rds"
) %>% 
  read_rds()

surveys_imputed <- here::here( # this data is for the d' measure
  "results",
  "data",
  "processed",
  "survey_scores_imputed.rds"
) %>% 
  read_rds()

```

# Describe sample

```{r}
ddf_vec <- paste(
  "tas",
  c("2", "4", "11", "12", "17"),
  sep = "_"
)


dif_vec = paste(
  "tas",
  c("1", "3", "6", "7", "9", "13", 14),
  sep = "_"
)

eot_vec = paste(
  "tas",
  c("5", "8", "10", "15", "16", "18", "19", "20"),
  sep = "_"
)

tas_vec <- paste(
  "tas", 
  c(1:20),
  sep = "_"
)

em_vec <- paste(
  "em", 
  c("01", "02", "03", "04", "05", "06"),
  sep = "_"
)

ae_vec <- paste(
  "ae",
  c("01", "05", "07"),
  sep = "_"
)

pa_vec <- paste(
  "pa",
  c("03", "06", "07"),
  sep = "_"
)

mt_vec <- paste(
  "mt",
  c("01", "02", "06"),
  sep = "_"
)
```

```{r}
jl_alpha <- function(data, vars){
  psych::alpha(select(data,
                      vars))$total$raw_alpha
}
```


```{r}
describe <- surveys_imputed %>% 
  transmute(
    age = age,
    ddf = select(., ddf_vec) %>% rowSums(na.rm = TRUE),
    dif = select(., dif_vec) %>% rowSums(na.rm = TRUE),
    eot = select(., eot_vec) %>% rowSums(na.rm = TRUE),
    tas = select(., tas_vec) %>% rowSums(na.rm = TRUE),
    msi_em = select(., em_vec) %>% rowSums(na.rm = TRUE),
    msi_ae = select(., ae_vec) %>% rowSums(na.rm = TRUE),
    msi_pa = select(., pa_vec) %>% rowSums(na.rm = TRUE),
    msi_mt =select(., mt_vec) %>% rowSums(na.rm = TRUE)
  ) %>% 
  psych::describe() %>% 
  data.frame() %>% 
  select(
    n, 
    mean,
    sd
  ) %>% 
  rownames_to_column("variable") %>%
  mutate(
    alpha = case_when(
      variable == "ddf" ~ jl_alpha(surveys_imputed, ddf_vec),
      variable == "dif" ~ jl_alpha(surveys_imputed, dif_vec),
      variable == "eot" ~ jl_alpha(surveys_imputed, eot_vec),
      variable == "tas" ~ jl_alpha(surveys_imputed, tas_vec),
      variable == "msi_em" ~ jl_alpha(surveys_imputed, em_vec),
      variable == "msi_ae" ~ jl_alpha(surveys_imputed, ae_vec),
      variable == "msi_pa" ~ jl_alpha(surveys_imputed, pa_vec),
      variable == "msi_mt" ~ jl_alpha(surveys_imputed, mt_vec)
    )
  )


describe %>% 
  knitr::kable("html") %>% 
  kableExtra::kable_styling()
```

# Correaltions 


```{r}

cor_data <- surveys_imputed %>% 
  select(
    age,
    tas:mt
  ) %>% 
  mutate(
    age = as.numeric(age)
  ) %>% 
  drop_na()

ggcorrplot::ggcorrplot(
  corr = cor(cor_data),
  method = "circle",
  colors = c("red", "grey", "blue"),
  type = "lower",
  lab = TRUE,
  p.mat = ggcorrplot::cor_pmat(cor_data),
  insig = "blank"
)
```

# Reaction Time Models 

```{r, include = FALSE}
rt_models <- list.files(here::here("results", "models", "rt", "raw"), full.names = TRUE, recursive = T)

rt_models

rt_block <- read_rds(rt_models[1])
rt_block_tas <- read_rds(rt_models[2])
rt_block_tas_emo <- read_rds(rt_models[3])
```

I have fit three models with increasing complextity. The first model contains the fixed effect for target stimulus type only. The second model adds an interaction between target stimulus type and alexithymia. The third model adds an interaction between target stimulus type and musical emotion abilities as measured by the Goldsmiths MSI. 

As can be seen in the model comparison the best fitting model is the model that contains the term for target stimulus type. 

```{r}
anova(rt_block, rt_block_tas, rt_block_tas_emo) %>%
  knitr::kable("html") %>%
  kableExtra::kable_styling()
```

Here the estimated marginal means for the fixed effect of target stimulus can be seen along with pairwise comparisons

```{r}
rt_emmeans <- emmeans::emmeans(rt_block, ~block)

pairs(rt_emmeans)

emmeans::emmip(rt_block,
  ~block,
  plotit = FALSE
) %>%
  ggplot2::ggplot(
    aes(
      x = block,
      y = yvar
    )
  ) +
  ggplot2::geom_point() +
  ggplot2::geom_errorbar(
    aes(
      ymin = yvar - SE,
      ymax = yvar + SE,
      width = .2
    )
  ) +
  ggplot2::xlab("Target Stimulus Type") +
  ggplot2::ylab("Reaction Time (ms)") +
  ggplot2::scale_x_discrete(labels = c("Word", "Face", "Music")) +
  ggplot2::theme_classic()
```

We can also see that the pattern of results remains consistent when using the imputed data. 

```{r, include = FALSE}
rt_imputed_models <- list.files(here::here("results", "models", "rt", "imputed"), full.names = TRUE, recursive = T)

rt_imputed_models

rt_imputed_block <- read_rds(rt_imputed_models[1])
rt_imputed_block_tas <- read_rds(rt_imputed_models[2])
rt_imputed_block_tas_emo <- read_rds(rt_imputed_models[3])
```

```{r}
anova(rt_imputed_block, rt_imputed_block_tas, rt_imputed_block_tas_emo) %>%
  knitr::kable("html") %>%
  kableExtra::kable_styling()
```

```{r}
rt_imputed_emmeans <- emmeans::emmeans(rt_imputed_block, ~block)

pairs(rt_imputed_emmeans)

emmeans::emmip(rt_imputed_block,
  ~block,
  plotit = FALSE
) %>%
  ggplot2::ggplot(
    aes(
      x = block,
      y = yvar
    )
  ) +
  ggplot2::geom_point() +
  ggplot2::geom_errorbar(
    aes(
      ymin = yvar - SE,
      ymax = yvar + SE,
      width = .2
    )
  ) +
  ggplot2::xlab("Target Stimulus Type") +
  ggplot2::ylab("Reaction Time (ms)") +
  ggplot2::scale_x_discrete(labels = c("Word", "Face", "Music")) +
  ggplot2::theme_classic()
```

## Summary 

To summarise the results, across both the raw and imputed data show that participants were faster to make judgements about whether the emotion in the cue and target stimulus were fastest when the target stimulus was a word compared to both a face and a musical excerpt. Further, participants were faster to make a decision about matching when the target stimulus was a face compared to when it was a song. 


# Accuracy Models 

```{r}
acc_models <- list.files(here::here("results", "models", "d_prime", "raw"), full.names = TRUE)

acc_models


d_block <- read_rds(acc_models[1])
d_block_tas <- read_rds(acc_models[2])
d_block_tas_emo <- read_rds(acc_models[3])
```

We can see here that the best fitting model is the model that includes the interaction between alexithymia and the stimulus type of the target. 

```{r}
anova(d_block, d_block_tas, d_block_tas_emo) %>%
  knitr::kable("html") %>%
  kableExtra::kable_styling()
```

Similar to the reaction time data we can see that participants performed best when the target stimulus was a word. Contrary to the reaction time data paricipants were equal in their performance on music and face targets

```{r}
d_emmeans <- emmeans::emmeans(d_block_tas, ~block)

pairs(d_emmeans)
```

Here we can see that alexithymia predicts worse performance across all stimulus types. However, the difference in slopes was not significant, although significance was approached for the contrast between the slope of alexithymia in the word condition compared to the slope for the music condition
```{r}
d_int <- emmeans::emtrends(d_block_tas, ~block, var = "tas_z")

d_int

interactions::interact_plot(d_block_tas, pred = "tas_z", modx = "block", legend.main = "Target stimulus type", modx.labels = c("Word", "Face", "Music")) +
  ggplot2::theme_classic() +
  ggplot2::xlab("Alexithymia (z-score)") +
  ggplot2::ylab("Accuracy(*d'*)") +
  ggplot2::theme(axis.title.y = ggtext::element_markdown()) +
  ggplot2::theme_classic()

pairs(d_int)
```

```{r}
acc_imputed_models <- list.files(here::here("results", "models", "d_prime", "imputed"), full.names = TRUE)

acc_imputed_models


d_imputed_block <- read_rds(acc_models[1])
d_imputed_block_tas <- read_rds(acc_models[3])
d_imputed_block_tas_emo <- read_rds(acc_models[2])
```

When looking at the imputed data we can see the best fitting model in the model that includes the interaction between alexithymia and stimulus type along with the interaction between stimulus typoe and the emotion measure from the GoldMSI

```{r}
anova(d_imputed_block, d_imputed_block_tas, d_imputed_block_tas_emo) %>%
  knitr::kable("html") %>%
  kableExtra::kable_styling()
```

First I will see if the pattern of results changes when looking at the model that has only the interaction between stimulus type and the alexithymia


```{r}
d_tas_imputed_emmeans <- emmeans::emmeans(d_imputed_block_tas, block)

pairs(d_emmeans)
```

Here we can see that alexithymia predicts worse performance across all stimulus types. However, the difference in slopes was not significant, although significance was approached for the contrast between the slope of alexithymia in the word condition compared to the slope for the music condition
```{r}
d_int <- emmeans::emtrends(d_block_tas, ~block, var = "tas_z")

d_int

interactions::interact_plot(d_block_tas, pred = "tas_z", modx = "block", legend.main = "Target stimulus type", modx.labels = c("Word", "Face", "Music")) +
  ggplot2::theme_classic() +
  ggplot2::xlab("Alexithymia (z-score)") +
  ggplot2::ylab("Accuracy(*d'*)") +
  ggplot2::theme(axis.title.y = ggtext::element_markdown()) +
  ggplot2::theme_classic()

pairs(d_int)
```

